**Measuring Depression and Anxiety with 4 items? Adaptation of the PHQ-4 to increase its Sensitivity to Subclinical Variability**

### 2024-12-13 paper/4_WIP/manuscript.qmd
updated manuscript

The original or refined version of the PHQ-4 was followed by the BDI-II, STAI-5, IAS, and MAIA-2, presented in random order. The IAS and the MAIA-2 were included as part of another study focused on interoception, and ere only used in this stud as part of data quality control checks.

>>>>

The original or refined version of the PHQ-4 was followed by the BDI-II, STAI-5, IAS, and MAIA-2, presented in random order. The IAS and the MAIA-2 were included as part of another study focused on interoception, and were only used in this stud as part of data quality control checks. 
## Results
